Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
cut substantially

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
\[
f: \UU_n \fg \to B
\]
be a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ lets us lift $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B_f)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

Existing work provides insight into and context for the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent algebras over $\Disk_n^\sqcup$.
\item In particular, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
Our approach leverages these results as follows to prove the theorem.
\begin{enumerate}
\item By modest extensions of the works cited above, we show that  $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-representations, which we also denote $B_f$. \owen{Let's hope we can justify this!}
\item Next, we transfer the question to the setting of {\em strict} $\Disk_n$-algebras that are weakly locally constant. 
Strictification theorems from the model category literature on operads say we can replace homotopy-coherent $\Disk_n$-algebras with strict ones. 
\item  In particular, given our $E_n$ algebra $B_f$ in $\fg$-modules, model it by a strict $\Disk_n$-algebra ${\tt B}_f$ with values in a nice model category $\Mod_\fg(\Ch_k)$ of dg $\fg$-representations.
The forgetful functor $\Mod_\fg(\Ch_k) \to \Ch_k$ lets us produce a strict prefactorization algebra ${\tt B}$ that models~$B$.
\item By construction, the action of $\fg$ on ${\tt B}_f$ determines a map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras that models the original map~$f$.
\item We then construct an explicit strict $\Disk_n$-algebra $\clies(\Omega \otimes \fg, {\tt B}_f)$ as a kind of ``convolution algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map
\[
\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
\]
such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict $\Disk_n$-algebras. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated $E_n$ algebras.

@@

By Knudsen's results \cite{Knudsen}, we have the following explicit applications of our main theorem~\ref{thm: center}.

\owen{I think we should just work in $Ch(\RR)$ or $Ch(\CC)$ throughout.}

\begin{cor}\label{cor:centerfactorization}
Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
Then the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
\end{cor}

@@

Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]

For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

\owen{Commented out below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}
%
%Our novel contribution in this paper is the following large $N$ result. Let $A$ be a unital algebra over a field $k$ of characteristic zero, 
%and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$. 
%The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
%
%\begin{thm}
%\label{thm: large N}
%The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
%\[
%\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
%\]
%down to an $E_n$ algebra.
%
%When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
%\[
%\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
%\]
%to each open set $U \subset \RR^n$.
%\end{thm}
%\greg{Shall we keep these examples which uses/but are the easy part/ of LQT theorem ?}
%\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}
%
%We can calculate the factorization homology of this factorization algebra explicitly.
%

@@

See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
which integrates all those actions and through which they all factor. 
As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.

\owen{I commented out a discussion of the factorization algebra version of centralizer, as I don't think it's relevant.}

%
%There is an immediate analogue of the notion of centralizers for factorization algebras.
%\begin{dfn}\label{D:centralizerFacAlgebra}
% Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
%The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
%algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
%\[
%\begin{tikzcd}
%& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
%A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
%\end{tikzcd}
%\]
%where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset. The {\em center} of a locally constant  factorization algebra
%$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
%\end{dfn}
%By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
%\begin{lmm}\label{L:faccentralizerexists}
% Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
% an $E_n$-algebra morphism $f:A\to B$, then 
% ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
% the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
%\end{lmm}
%

%We now turn to proving Theorem~\ref{thm: centralizer}.

\section{Lifting $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules}

A technical result is the key step.

\def\obl{{\rm obl}}

\begin{prp}
\label{prp: def of obl}
For $\fg$ a dg Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
there is a forgetful functor $\obl: \Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ that is lax $E_n$-monoidal.
\end{prp}

\owen{I don't know if we need to include the adjective ``lax'' here, or if it's implicit in the usual discussions these days.}

Concretely, we mean there is a natural morphism
\[
\obl(M) \otimes_k \obl \to \obl(M \otimes_{\UU_n \fg} N) 
\]
as left modules over $U\fg$, i.e., as $\fg$-representations.

As a consequence, we obtain the following.

\begin{cor}
There is a functor 
\[
\Alg_{E_n}(\obl): \Alg_{E_n}({\Mod^{E_n}_{\UU_n \fg}}) \to \Alg_{E_n}(\LMod_{U\fg}).
\]
\end{cor}

These results can be marshaled to prove the first bullet point of our main theorem.

\begin{prp}
Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, 
and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
Given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
\end{prp}

That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.

\begin{proof}
By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules with monoidal structure $\otimes_B$. 
Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
(See also Example 3.4.4.7 of the same reference.)
In other words, there is an object $\Hat{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.

Given a map of $E_n$-algebras $f : A \to B$, 
the forgetful functor of $E_n$-module categories 
\[
f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
\]
admits a natural refinement to an $E_n$-monoidal functor.
\owen{Any place to cite?}
In particular, for $A = \UU_n \fg$, there is an $E_n$-algebra object $f^*\Hat{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$, and it forgets to $B$ under the forgetful functor to $\Ch_k^{\otimes_k}$, by construction.

Applying the $E_n$-monoidal functor $\obl$, we obtain an $E_n$ algebra $\obl(f^*\Hat{B})$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$.
Again, by construction, it forgets to $B$.
We denote $\obl(f^*\Hat{B})$ by~$B_f$.
\end{proof}

\begin{rmk}
By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
As the forgetful functor $\Alg_\Lie({\tt Ch}_k) \to \Alg_\Lie({\tt Ch}_k)$ is \owen{more adjectives},
we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
Moreover, there is a canonical map ${\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
\end{rmk}

It remains to prove the technical result.\owen{We are stuck on this point.}

\begin{proof}[Proof of proposition~\ref{prp: def of obl}]
We construct the underlying functor of $\infty$-categories $\Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ 
before lifting to a lax $E_n$-monoidal functor.

For any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), 
there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is 
\[
\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right),
\] 
where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}).
% = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
Consider now the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$,
which induces a forgetful functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
The composite 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) \xto{i^*}  {\rm LMod}_{U\fg} (\Ch_k^{\otimes_k})
\]
is the desired forgetful functor.

\owen{Now we need to explain why it is lax monoidal.}
\end{proof}

%\section{Strictifying the map $f: \UU_n \fg \to B$}
%
%
%\owen{If our new strategy works, then we can get rid of this section.}
%
%As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
%
%By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
%\[
%{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
%\]
%
%\owen{And now I'm really confused.}
%
%\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
%
%
%\begin{rmk}
%It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
%the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
%Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
%that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
%\end{rmk}
%
%Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
%\[
%\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
%\]
%gives a $L_\infty$-algebra morphism 
%\begin{equation}
% \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
%\end{equation}
%which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
%
%\brian{let's start with a strict representative $B$. 
%So we have an actual locally constant factorization algebra.}
%
%\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
%The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
%\end{prp}
%\begin{proof}
% 
%\end{proof}
%Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
%Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
%we obtain an induced map of factorization 
%algebras 
%\begin{equation}\label{eq:DefofFonFaclevel}
% \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
%\end{equation}
% where $B(-)$ is the factorization algebra associated to $B$.
% \brian{How about $\ul{B}$ instead?}
% 
%\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
% $\fg \otimes \Omega^*_c(-)$.
%\end{lmm}
%\begin{proof}
% 
%\end{proof}
%The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
%$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
%of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
%a finite family of pairwise disjoint open subsets of an open $V$, by 
%\begin{multline}\label{eq:transClieFac}
% \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
% \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
% \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
% \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
% = \cliels(\fg\otimes \Omega_c(V), B(V))
%\end{multline}
%where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
%
%\smallskip
%
%The (homotopy) sheaf structure of forms also gives us structure maps
%\begin{multline}\label{eq:transClieFacCochain}
% \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
%  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \stackrel{\mu_B}\longrightarrow 
%  \clies(\fg\otimes \Omega (V), B(V))
%\end{multline}
%where $\rho$ is given by the restriction of forms onto a subspace. 
%
%\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
% the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
% Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
% $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
%\end{lmm}
%\begin{dfn}\label{dfn:CEofFact}
%We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
%and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.

>>>>

Even to state our central result, we need to review a few results and terminology.
First, our basic context is $E_n$ algebras.
By $E_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads. 
In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
For us the preferred presentation is by locally constant factorization algebras on $\RR^n$,
which, as we explain below, can be understood via a colored operad whose colors are open sets in~$\RR^n$.

Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks to Knudsen \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh))
\]
equipped with a convolution-type product.
\end{thm}

\owen{I think we could (and maybe should) also discuss the $E_n$-Koszul dual situation involving cochains.}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item In particular, in addition to the factorization algebra model, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item From the map $f: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$, 
we produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \UU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to Z_f
\]
as factorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

@@

If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $E_n$ algebras.
In this case, we obtain a version of Koszul duality as the corollary.

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $E_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

@@

See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
which integrates all those actions and through which they all factor. 
As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.

We now turn to proving Theorem~\ref{thm: centralizer}.

\section{}

The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace.

\label{L:ClieFacDef} 
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.

\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

\section{Convolution algebras over colored operads}

\def\conv{{\rm Conv}}

\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}

\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}

\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
